TBD

### 2021-03-22 outputs/paper/paper.Rmd
updated S8 regression model

# code dummy variables
s8_model <- dfBehavModel
s8_model$cond <- ifelse(s8_model$cond < 1, 0, 1)

@@

# final table (S8)
stargazer(s8_main_result, s8_money_result, 
          title = "Reporting rates in the Money and No Money Condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Male", "Above 40", "Computer", "Coworkers", "Other Bystanders", "Constant"),
          column.labels = c("No Money", "Money"))

>>>>

# code dummy variables
s8_model <- dfBehavModel %>%
  filter(cond != 0)
s8_model$cond <- ifelse(s8_model$cond == 1, 0, 1)

@@

# final table (S8)
stargazer(s8_main_result, s8_money_result, 
          title = "Reporting rates in the Money and No Money Condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Male", "Above 40", "Computer", "Coworkers", "Other Bystanders", "Constant"))
